Fitting Synchrotron Models to Gamma-Ray Burst Data from INTEGRAL/SPI

### 2021-11-29 src/ms.tex
text

As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement. Therefor we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.

>>>>

As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement. Therefore we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.
